---
title: "HomeWork3"
author: "ThoTho Totokani"
date: "September 15, 2018"
output: html_document



---
###Installed packages:"fivethirtyeight") ,"vcdExtra","rplyr","plyr","ggplo2"

#1. The code I used to create a new directory, navigate to my directory, and clone the repositorym to it with Git.


#2.	Data Summary (20 points): From this aforementioned cloned repo, please extract titanic.csv.zip.  To be clear, this does not have to be done in Git or command line.  

##a.Read in titanic.csv via read.csv(), 

```{r}

Mydate=read.csv("titanic.csv", header=TRUE )
names(Mydate)

df=data.frame(Mydate)
str(df)
t<-df

```

##b.Output  count of females and males aboard the Titanic. 
```{r}
Mydata=read.csv("titanic.csv", header=TRUE)

#question b

##.	Output of the respective count of females and males aboard the Titanic.

sum=(Mydata$Sex=='female')
sum=(Mydata$Sex=='male')
##Plot  ofthe frequency of females and males.  Be sure to give an accurate title and label the axes.
plot(Mydata$Sex, main='Frequency of Male and Female', xlab='Gender', ylab='Number')


```

##c.	Please use one apply function (to review: swirl() modules 11, 12) to output the means of Age, Fare, and Survival.  Make sure the output is a real number for all three means.

```{r}
names(Mydata)
sac<-function(x){ mean(x)}
Mydata$Age<-!is.na(Mydata$Age)
dap0<-data.frame(Mydata$Age, Mydata$Fare ,Mydata$Survived)
sapply(dap0,sac)
```




#3.	Function Building Load sleep_data_01.csv (found at http://talklab.psy.gla.ac.uk/L1_labs/lab_1/homework/index.html)

```{r}
# The Package("RCurl") Must be installed before this script run . If you get an error Install it manually before to run the script
#install.packages("RCurl")

install.packages("RCurl",repos = "http://cran.us.r-project.org")

library(RCurl)

myurl<-"http://talklab.psy.gla.ac.uk/L1_labs/lab_1/homework/sleep_data_01.csv"
x <-getURL(myurl)
## Or 
## x <- getURL(URL, ssl.verifypeer = FALSE)
t <-read.csv(textConnection(x))
head(t)

#This Line of script must be run on R to avoid error on Markdwon,It loads the file
download.file("http://talklab.psy.gla.ac.uk/L1_labs/lab_1/homework/sleep_data_01.csv",destfile="sleep_data_01.csv",method="libcurl")

```
##a.	Create objects for the median Age, the minimum and maximum Duration of sleep, and the mean and standard deviation of the Rosenberg Self Esteem scale (RSES).

##b.	Create a data.frame object called report: it should consist of the median age, the RSES mean and standard deviation respectively divided by five (since there are five questions and these scores are summed), and the range of Duration (the statistical definition of range; it should be a single number.)

#c.	Change the column names of this data.frame to MedianAge, SelfEsteem, SE_SD, and DurationRange.
#d.	Round the report to at most 2 digits: leave this as the closing line to the function.
#e.	Finally, run the function on your sleep data to show the output.


##
```{r}




# Compute the Median of Age 

median(t$Age, na.rm=TRUE)

summary(t$Age)

#Compute the Min and Max of Sleep

 summary(t$Bedtime)
#Compute Standard deviation of RSES
sd(t$RSES , na.rm=TRUE)


median(t$Age, na.rm=TRUE)
tmed<-median(t$Age, na.rm=TRUE)


#Compute the Min and Max of Sleep
tmin<-min(t$Bedtime, na.rm=TRUE)

tmax<-max(t$Bedtime,na.rm=TRUE)
summary(t$Bedtime)

#Compute Standard deviation of RSES

tsd<-sd(t$RSES , na.rm=TRUE)/5

# Range of duration 


head(t)
dumax<-max(t$Duration,na.rm=TRUE)
dumin<-min(t$Duration,na.rm=TRUE)
durange<-max(t$Duration,na.rm=TRUE)-min(t$Duration,na.rm=TRUE)
range(t$Duration,na.rm=TRUE)

#Create Object Dataframe Report


report<-data.frame(tmed,tmin, tmax,tsd, durange)
head(report)
names(report)[1] <- "MedianAge"
names(report)[2] <- "SelfEsteem"
names(report)[4] <- "SE_SD"
names(report)[5] <- "DuratioRange"
head(report)



#c.	Change the column names of this data.frame to MedianAge, SelfEsteem, SE_SD, and DurationRange.

round(report, digits=2)


 
```




#4.	FiveThirtyEight Data (30 points): Navigate on GitHub #https://github.com/rudeboybert/fivethirtyeight and read README.md. It will include #everything you need. 

```{r}




##a.a.	Install the fivethirtyeight package.
 ###install.packages("fivethirtyeight")
 ###install.packages("vcdExtra")

##b.	In the listing of Data sets in package 'fivethirtyeight,' assign the 22nd data set to an object 'df.'
 
vcdExtra::datasets("fivethirtyeight")



##b.	In the listing of Data sets in package 'fivethirtyeight,' assign the 22nd data set to an object 'df.'
 df <-college_recent_grads
 
 
#c.	Use a more detailed list of the data sets to write out the URL in a comment to the related news story.
 
 dim(college_recent_grads)
 
 names(df)
```

#5.	Data Summary (30 points): Use your newly assigned data frame from question 4 for this question. 

##a.	Write an R command that gives you the column names of the data frame.  Right after that, write one that counts the number of columns but not rows.  Hint: The number should match one of your numbers in Question 1d for dimensions.

```{r}
ncol(df)
names(df)

```
##b.	Generate a count of each unique major_category in the data frame.  I recommend using libraries to help.  To be clear, this should look like a matrix or data frame containing the major_category and the frequency it occurs in the dataset.  Assign it to major_count.
```{r}

Matr_df <- aggregate(major_code ~ major_category, df, length)
colnames(Matr_df)[2] <- "major_count"
Matr_df
```

##c.	To make things easier to read, put par(las=2) before your plot to make the text perpendicular to the axis.  Make a barplot of major_count.  Make sure to label the title with something informative (check the vignette if you need), label the x and y axis, and make it any color other than grey.  Assign the major_category labels to their respective bar.  Flip the barplot horizontally so that bars extend to the right, not upward.  All of these options can be done in a single pass of barplot(). Note: It's okay if it's wider than the preview pane.


```{r}
dtx <- Matr_df$major_count
par(las=2)
barplot(dtx, names.arg = Matr_df$major_category, horiz = TRUE, xlab ="NcountElements", main=" Major Category")

```

##d.	Write the fivethirtyeight data to a csv file.  Make sure that it does not have row labels.

```{r}
Sys.setenv(TZ='EST')

write.csv(df, file = "C:\\Datascience\\WH3\\thotho1.csv",row.names=FALSE, na="")
```



